---
title: "Data preparation"
output:
  html_document: default
  html_notebook: default
---

```{R,include=FALSE}
#source("lib/ggcorplot.R")
library(dplyr)
```

# Original data file

An Excel/OpenOffice Calc sheet is exported to single CSV files, which are described below.

Here are contents of the export directory:
```{bash}
ls -lh csv
```

* **evaluations** - contains webpage evaluations and their according textual justifications

```{R}
# Load data file -----
c3 <- list() # C3 data set
c3.evaluations <- read.csv("csv/evaluations.csv")
c3.sites <- read.csv("csv/sites.csv")
c3.labelers <- read.csv("csv/labelers.csv")
c3.tags <- read.csv("csv/tags.csv")
c3.golden <- read.csv("csv/golden_examples.csv")
c3.labelings <- read.csv("csv/evaluations_labelings.csv")
c3.labelings_exploded <- read.csv("csv/evaluations_labelings_exploded.csv")
```

## "Evaluations"

```{r}
glimpse(c3.evaluations)
```

Change column type:

* documentevaluation_id to factor
* document_id to factor
* documentevaluation_start to time
* documentevaluation_end to time
* documentevaluation_description  to character
* documentevaluation_comment to character
* documentevaluation_website1 to character
* documentevaluation_website2 to character
* documentevaluation_website3 to character
* documentevaluation_experience to boolean
* documentevaluation_opinion to boolean
* documentevaluation_knowledgable to boolean
* documentevaluation_baddescription to boolean
* documentevaluation_badcomment to boolean
* documentevaluation_badwebsites to boolean
* personexperimentround_id to factor

Drop column
rater_id.1

```{R}
# Change column types ----
c3.evaluations$documentevaluation_id <- as.factor(c3.evaluations$documentevaluation_id)
c3.evaluations$document_id <- as.factor(c3.evaluations$document_id)
#show_miliseconds <- options(digits.secs=6)
c3.evaluations$documentevaluation_start <- as.POSIXct(strptime(c3.evaluations$documentevaluation_start, "%Y-%m-%d %H:%M:%OS"))
c3.evaluations$documentevaluation_end <-  as.POSIXct(strptime(c3.evaluations$documentevaluation_end, "%Y-%m-%d %H:%M:%OS"))
c3.evaluations$documentevaluation_description <- as.character(c3.evaluations$documentevaluation_description)
c3.evaluations$documentevaluation_comment <- as.character(c3.evaluations$documentevaluation_comment)
c3.evaluations$documentevaluation_website1 <- as.character(c3.evaluations$documentevaluation_website1)
c3.evaluations$documentevaluation_website2 <- as.character(c3.evaluations$documentevaluation_website2)
c3.evaluations$documentevaluation_website3 <- as.character(c3.evaluations$documentevaluation_website3)
c3.evaluations$documentevaluation_experience <- as.logical(c3.evaluations$documentevaluation_experience)
c3.evaluations$documentevaluation_opinion <- as.logical(c3.evaluations$documentevaluation_opinion)
c3.evaluations$documentevaluation_knowledgeable <- as.logical(c3.evaluations$documentevaluation_knowledgeable)
c3.evaluations$documentevaluation_baddescription <- as.logical(c3.evaluations$documentevaluation_baddescription)
c3.evaluations$documentevaluation_badcomment <- as.logical(c3.evaluations$documentevaluation_badcomment)
c3.evaluations$documentevaluation_badwebsites <- as.logical(c3.evaluations$documentevaluation_badwebsites)
c3.evaluations$personexperimentround_id <- as.factor(c3.evaluations$personexperimentround_id)
```


```{R,options(width=50)}
glimpse(c3.evaluations)
```

If we are aware of any bugs in the data, we clean them.

```{r}
c3.evaluations$documentevaluation_credibility[c3.evaluations$documentevaluation_credibility>5] <- NA
```




## "Sites"

```{r}
glimpse(c3.sites)
```

Change column type:

* document_id to factor
* document_url to character
* document_category_id to factor

Drop column

* rater_id.1

```{R}
# Change column types ----
c3.sites$document_id <- as.factor(c3.sites$document_id)
c3.sites$document_url <- as.character(c3.sites$document_url)
c3.sites$document_category_id <- as.factor(c3.sites$document_category_id)
```


```{R}
glimpse(c3.sites)
```

## "Labelers"

```{r}
glimpse(c3.labelers)
```

Change column type:

* all to factors except is_test
* person_user_username as character 

```{R}
# Change column types ----
c3.labelers$person_id <- as.factor(c3.labelers$person_id)
c3.labelers$person_user_username <- as.character(c3.labelers$person_user_username)
colnames(c3.labelers)[3] <- "is_test"
c3.labelers$person_id <- as.factor(c3.labelers$person_id)
c3.labelers$person_user_username <- as.character(c3.labelers$person_user_username)
c3.labelers$is_test <- as.logical(c3.labelers$is_test)
c3.labelers$person_gender <- as.factor(c3.labelers$person_gender)
c3.labelers$person_birthyr <- as.factor(c3.labelers$person_birthyr)
c3.labelers$person_education <- as.factor(c3.labelers$person_education)
c3.labelers$person_wage <- as.factor(c3.labelers$person_wage)
c3.labelers$person_politics <- as.factor(c3.labelers$person_politics)
c3.labelers$person_state <- as.factor(c3.labelers$person_state)
c3.labelers$person_country <- as.factor(c3.labelers$person_country)
```


```{R}
glimpse(c3.labelers)
```

## "Tags"

```{r}
glimpse(c3.tags)
```

Change column type:

```{R}
# Change column types ----
c3.tags$tag_code <- as.factor(c3.tags$tag_code)
c3.tags$tag_label <- as.character(c3.tags$tag_label)
c3.tags$tag_group <- as.factor(c3.tags$tag_group)
```


```{R}
glimpse(c3.tags)
```


## "Golden examples"

```{r}
glimpse(c3.golden)
```

Change column type:


```{R}
# Change column types ----
c3.golden$documentevaluation_id <- as.factor(c3.golden$documentevaluation_id)
colnames(c3.golden)[2] <- "is_gold"
c3.golden$is_gold <- as.logical(c3.golden$is_gold)
c3.golden$gold_url <- as.character(c3.golden$gold_url)
c3.golden$tag_code <- as.factor(c3.golden$tag_code)

c3.golden %>% 
  select(-gold_category) %>%
  as.data.frame() -> c3.golden

c3.golden$gold_text <- as.character(c3.golden$gold_text)

c3.golden %>%
  left_join(c3.tags,by="tag_code") -> c3.golden
```


```{R}
glimpse(c3.golden)
```

## "Evaluation labelings"

```{r}
glimpse(c3.labelings)
```

Change column type:

```{R}
# Change column types ----

c3.labelings$commentlabeling_id <- as.factor(c3.labelings$commentlabeling_id)
c3.labelings$labeller_id <- as.factor(c3.labelings$labeller_id)
colnames(c3.labelings)[2] <- "person_id"
c3.labelings$rater_id <- as.factor(c3.labelings$rater_id)
c3.labelings$documentevaluation_id <- as.factor(c3.labelings$documentevaluation_id)
c3.labelings$document_id <- as.factor(c3.labelings$document_id)
#show_miliseconds <- options(digits.secs=6)
c3.labelings$start <-  as.POSIXct(strptime(c3.labelings$start, "%Y-%m-%d %H:%M:%OS"))
c3.labelings$end <-  as.POSIXct(strptime(c3.labelings$end, "%Y-%m-%d %H:%M:%OS"))
c3.labelings$answer <- as.character(c3.labelings$answer)
c3.labelings$rejected <- as.logical(c3.labelings$rejected)
c3.labelings$is_test. <- as.logical(c3.labelings$is_test.)
colnames(c3.labelings)[10] <- "is_test"
c3.labelings$is_gold. <- as.logical(c3.labelings$is_gold.)
colnames(c3.labelings)[11] <- "is_gold"
c3.labelings$is_finished. <- as.logical(c3.labelings$is_finished.)
colnames(c3.labelings)[12] <- "is_finished"
c3.labelings$is_ok. <- as.logical(c3.labelings$is_ok.)
colnames(c3.labelings)[13] <- "is_ok"
c3.labelings$documentevaluation_id <- as.factor(c3.labelings$documentevaluation_id)
colnames(c3.golden)[2] <- "is_gold"
```

```{R}
glimpse(c3.labelings)
```


## "Evaluation labelings exploded"

```{r}
glimpse(c3.labelings_exploded )
```

Change column type:

```{R}
# Change column types ----
c3.labelings_exploded %>%
  select(-is_ok.,-labelcat) -> c3.labelings_exploded
c3.labelings_exploded$commentlabeling_id <- as.factor(c3.labelings_exploded$commentlabeling_id)
c3.labelings_exploded$person_id <- as.factor(c3.labelings_exploded$person_id)
c3.labelings_exploded$documentevaluation_id <- as.factor(c3.labelings_exploded$documentevaluation_id)
c3.labelings_exploded$document_id <- as.factor(c3.labelings_exploded$document_id)
c3.labelings_exploded$category <- as.character(c3.labelings_exploded$category)
c3.labelings_exploded$label <- as.factor(c3.labelings_exploded$label)
```

```{R}
glimpse(c3.labelings_exploded)
```


